Next Trippy Structures\thanks{Supported by organization x.}

### 2019-02-21 paper.tex
Update on Overleaf.
Satisfied with plots

>>>>

\begin{figure}[hbt!]
\includegraphics[width=0.5\textwidth]{experiments/board.eps}
\caption{Comparison of \texttt{board\_X$_{LT}$} queries, with all variants}
\end{figure}

\begin{figure}[hbt!]
\includegraphics[width=0.495\textwidth]{experiments/start.eps}
\includegraphics[width=0.495\textwidth]{experiments/end.eps}
\caption{Comparison of \texttt{start\_X$_{LT}$} (left) and \texttt{end\_X$_{LT}$} (right) queries, with all variants}
\end{figure}

\begin{figure}[hbt!]
\includegraphics[width=0.495\textwidth]{experiments/xy0.eps}
\includegraphics[width=0.495\textwidth]{experiments/xy1.eps}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (left) and starting time (right) restrictions}
\end{figure}

\begin{figure}[hbt!]
\includegraphics[width=0.495\textwidth]{experiments/xy2.eps}
\includegraphics[width=0.495\textwidth]{experiments/xy3.eps}
\caption{Comparison of \texttt{from\_X$_{LT}$\_to\_Y$_{LT}$} queries, variating line (left) and starting time (right) restrictions with a fixed ending time restriction}
\end{figure}
